\Large\textbf{Preparation GUIDE for Initial-Submission Manuscript}\\~\\ \large\textbf{ Preparation of Papers in Two-Column Format\\ for the ASP-DAC 2014 (\LaTeX2e version)}

### 2014-01-28 discussion.tex
Updated

\begin{figure}[h!]
  \centering
	\vspace{-10pt}
        \begin{lstlisting}[style=sysj,basicstyle=\normalsize\ttfamily,morekeywords={emit,trap,pause,exit,wait_exact}]
          while(true){wait_exact (1 ms); emit S; //do something
          }
 \end{lstlisting}
  \caption{Programming periodic tasks with wait\_exact statement}
  \label{fig:periodic}
	\vspace{-10pt}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \begin{SubFloat}{\label{pp:a}Original program}
    \centering
			\begin{lstlisting}[style=sysj,basicstyle=\normalsize\ttfamily,morekeywords={emit,trap,pause,exit,wait_exact}]
while(true) {
 wait_exact(1 ms);
 //extra pause
 pause;
 emit S;
}
\end{lstlisting}
\end{SubFloat}
\hspace{9pt}
  \begin{SubFloat}{\label{pp:b}Rewritten program}
			\begin{lstlisting}[style=sysj,basicstyle=\normalsize\ttfamily,morekeywords={emit,trap,pause,exit,delay}]
while(true) {
 while(true) { 
  trap(T) {
   int x = 0;
   while(true) {
    x = x + 1;
    pause;
    if (x == d)
     exit(T);
   }
  }
  //extra pause
  pause;
  emit S;
 }
}
\end{lstlisting}
  \end{SubFloat}
\caption{Extra pause statements in periodic tasks}
  \label{fig:periodic2}
\end{figure}

@@

\begin{figure}[h!]
  \centering
	\vspace{-10pt}
		\begin{lstlisting}[style=sysj,basicstyle=\normalsize\ttfamily,morekeywords={emit,trap,pause,exit,delay,suspend}]
suspend(S) {
 emit START_TIMER(10); 
 await (TIMER);emit O1;
}
		\end{lstlisting}
  \caption{Interaction of preemption and external timers}
  \label{fig:preemp}
	\vspace{-10pt}
\end{figure}

@@

\begin{figure}[h!]
  \centering
	\vspace{-10pt}
		\begin{lstlisting}[style=sysj,basicstyle=\normalsize\ttfamily,morekeywords={emit,trap,pause,exit,delay,suspend}]
{
 //reaction R1
 emit START_TIMER(1 ms); 
 await (TIMER);emit O1;
}
|| //synchronous parallel
{
 //reaction R2
 // do something
}
		\end{lstlisting}
  \caption{Resolution of external timers}
  \label{fig:resolution}
	\vspace{-10pt}
\end{figure}

>>>>

\begin{figure}[h!]
	\vspace{-10pt}
        \begin{lstlisting}[style=sysj,basicstyle=\footnotesize\ttfamily,morekeywords={emit,trap,pause,exit,wait_exact}]
while(true){wait_exact (1 ms); 
	emit S; //do something
}
 \end{lstlisting}
  \caption{Programming periodic tasks with wait\_exact statement}
  \label{fig:periodic}
	\vspace{-10pt}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \begin{SubFloat}{\label{pp:a}Original program}
    \centering
			\begin{lstlisting}[style=sysj,basicstyle=\footnotesize\ttfamily,morekeywords={emit,trap,pause,exit,wait_exact}]
while(true) {
 wait_exact(1 ms);
 //extra pause
 pause;
 emit S;
}
\end{lstlisting}
\end{SubFloat}
\hspace{9pt}
  \begin{SubFloat}{\label{pp:b}Rewritten program}
			\begin{lstlisting}[style=sysj,basicstyle=\footnotesize\ttfamily,morekeywords={emit,trap,pause,exit,delay}]
while(true) {
 while(true) { 
  trap(T) {
   int x = 0;
   while(true) {
    x = x + 1;
    pause;
    if (x == d)
     exit(T);
   }
  }
  //extra pause
  pause;
  emit S;
 }
}
\end{lstlisting}
  \end{SubFloat}
\caption{Extra pause statements in periodic tasks}
  \label{fig:periodic2}
\end{figure}

@@

\begin{figure}[h!]
  \centering
	\vspace{-10pt}
		\begin{lstlisting}[style=sysj,basicstyle=\footnotesize\ttfamily,morekeywords={emit,trap,pause,exit,delay,suspend}]
  suspend(S) {
   emit START_TIMER(10); 
   await (TIMER);emit O1;
  }
		\end{lstlisting}
  \caption{Interaction of preemption and external timers}
  \label{fig:preemp}
	\vspace{-10pt}
\end{figure}

@@

\begin{figure}[h!]
  \centering
	\vspace{-10pt}
		\begin{lstlisting}[style=sysj,basicstyle=\footnotesize\ttfamily,morekeywords={emit,trap,pause,exit,delay,suspend}]
{
 //reaction R1
 emit START_TIMER(1 ms); 
 await (TIMER);emit O1;
}
|| //synchronous parallel
{
 //reaction R2
 // do something
}
		\end{lstlisting}
  \caption{Resolution of external timers}
  \label{fig:resolution}
	\vspace{-10pt}
\end{figure}

### 2014-01-28 exps.tex
Updated

\hj{
HRTCS is the human response system described in
Section~\ref{sec:motivating-example}. }

\hj{
Motor is a stepper motor
controller from~\cite{Bourke2009a}, used for producing monochrome images
on paper by correct application of current to a print head (a row of
resistors). In this example, duration of the current applied is
controlled by the feedback logic using real-time waits, which are
expressed using reactive constructs. }

\hj{
Printer is an example
from~\cite{Schneider:1999:CRT:555233}, which models a printer and a
spooler in timed CSP. Its operation can be described as follows: as soon
as the spooler receives a print job it passes it to the printer through
a channel where actual printing process take place. This example along
with HRTCS demonstrates the use of non exact wait statements.
}

AECS (Access and Environmental Control System) is an application that
controls an intelligent room environment described
in~\cite{aecs_ispa}. The system interacts with two external timers
through input/output signals in order to measure how long the entrance
door to the room is being opened to detect intruders.  The program has
been modified such that the wait constructs are used instead of external
timers as shown in Figure~\ref{delaycode}. In the original AECS, the
system needed to trigger an external timer by emitting the output signal
in order to wait for a specific amount of time (e.g.
\texttt{TimerTriggered} in Figure~\ref{delaycode:a}). When the timer
expires, it notifies the system through the input signal
\texttt{TimeOut}, which is polled using the \texttt{await}
statement. With the new wait constructs, these timers are not necessary
and waits can be expressed directly in the code as shown in
Figure~\ref{delaycode:b}.

@@

HRTCS consists of 2 CDs, but only one with real-time waits. AECS also
has 2 CDs; CD1 consist of a single wait statement, while CD2 has 2 wait
statements. In this case, as explained previously, wait statements
replace the external timers and corresponding interface (I/O)
signals. The system triggers an alarm 10 seconds after detection of an
intruder or generates a beep sound when an entrance door is being opened
for the same amount of time. In the Printer example, spooler and printer
processes are mapped to separate CDs. Spooler CD sends a job to the
Printer CD between 2.7 to 10.6 ms after receiving it from the
environment (e.g. a user). On the other hand, Printer CD notifies the
environment that it starts printing between 1.2 to 30.3 ms once it
receives the job from the Spooler CD. Actual print job is started
between 5.6 to 100.2 ms after the notification. In this example, bounded
wait ensures that both; channel communication and print job should occur
within the specified amount of time. Lastly, Motor is a synchronous
program with 5 exact wait statements that control the amount of current
applied to the stepper motor coils.

@@

\begin{figure}[h!]
	\centering
\begin{tikzpicture}[scale=0.9]
	\begin{axis}[
			ybar,xtick=data,
			symbolic x
			coords={HRTCS,Printer/CD1,Printer/CD2,AECS/CD2},
			height=5cm,
			width=9.5cm,
			minor y tick num=1,
			yminorgrids=true,
			ymajorgrids=true,
			ytick={0,0.5,...,2},
			enlarge x limits=0.3,
%      xlabel=Benchmark,
			x tick label style={rotate=45,font=\footnotesize},
			ylabel=Difference factor,
		]
			\addplot + [postaction={pattern=north east lines}] coordinates
			{(HRTCS,1)(Printer/CD1,1)(Printer/CD2,1)(AECS/CD2,1.94)};
			\addplot + [postaction={pattern=north west
                          lines}] coordinates 
                        {(Printer/CD2, 1)(AECS/CD2, 1.94)};
	\end{axis}
\end{tikzpicture}
\begin{tikzpicture}[scale=0.9]
	\begin{axis}[
			ybar,xtick=data,
			symbolic x coords={Motor},
			ytick={0,0.5,...,5},
			ymin={1.5},
			minor y tick num=1,
			yminorgrids=true,
			ymajorgrids=true,
%      extra y ticks={2.5},
%      extra y tick labels={asdf},
%      extra y tick style={grid=major},
			height=5cm,
			width=9.5cm,
			xlabel=Benchmark,
			xlabel shift={4pt},
			ylabel=Difference factor,
			legend style={
				anchor=north,
				at={(0.45,-0.44)},
				legend columns=-1,
			}
%      nodes near coords
		]
			\addplot + [postaction={pattern=north east lines}] coordinates
                        {(Motor, 2.60)};
			\addplot + [postaction={pattern=north west lines}] coordinates
                        {(Motor, 2.63)};
			\addplot + [postaction={pattern=dots}] coordinates
                        {(Motor, 4.39)};
			\addplot + [postaction={pattern=horizontal lines}] coordinates
                        {(Motor, 2.92)};
			\addplot + [postaction={pattern=crosshatch}] coordinates
                        {(Motor, 2.69)};
			\legend{Delay1,Delay2,Delay3,Delay4,Delay5}
	\end{axis}
\end{tikzpicture}
\caption{Accuracy of the results}
\label{fig:graph1}
\end{figure}

@@

\begin{figure}[ht!]
	\centering
%\begin{tikzpicture}[scale=0.9]
%  \begin{axis}[
%      ybar,xtick=data,
%      symbolic x
%      coords={AECS/CD2},
%      height=5cm,
%      width=9.5cm,
%      minor y tick num=1,
%      yminorgrids=true,
%      ymajorgrids=true,
%      xlabel=Benchmark,
%      ylabel=Percentage reduction,
%    ]
%      \addplot coordinates
%      {(AECS/CD2, 11.82)};
%  \end{axis}
%\end{tikzpicture}
\begin{tikzpicture}[scale=0.9]
	\begin{axis}[
			ybar,xtick=data,
			symbolic x coords={Motor,AECS/CD2},
			ytick={0,1,...,12},
			ymin={6},
			minor y tick num=1,
			enlarge x limits=0.5,
			enlarge y limits=0.1,
			yminorgrids=true,
			ymajorgrids=true,
			height=7cm,
			width=9.5cm,
			xlabel=Benchmark,
			xlabel shift={4pt},
			ylabel=Percentage reduction (\%),
			legend style={
				anchor=north,
				at={(0.45,-0.29)},
				legend columns=-1,
			}
		]
			\addplot + [fill=white,postaction={pattern=north east lines}] coordinates
                        {(Motor, 8.05) (AECS/CD2, 11.82)};
			\addplot + [fill=white,postaction={pattern=north west lines}] coordinates
                        {(Motor, 8.00) (AECS/CD2, 11.82)};
			\addplot + [fill=white,postaction={pattern=dots}] coordinates
                        {(Motor, 6.42)};
			\addplot + [fill=white,postaction={pattern=horizontal lines}] coordinates
                        {(Motor, 7.53)};
			\addplot + [fill=white,postaction={pattern=crosshatch}] coordinates
                        {(Motor, 7.89)};
			\legend{Delay1,Delay2,Delay3,Delay4,Delay5}
	\end{axis}
\end{tikzpicture}
\caption{Reduction in upper bound relaxation with improved WCRT}
\label{fig:graph2}
\end{figure}

>>>>

\hj{ HRTCS is the human response system described in
	Section~\ref{sec:motivating-example}. HRTCS consists of 2 CDs, but
only one with real-time waits.}

\hj{ Motor is a stepper motor controller from~\cite{Bourke2009a}, used
for producing monochrome images on paper by correct application of
current to a print head (a row of resistors). In this example, duration
of the current applied is controlled by the feedback logic using
real-time waits, which are expressed using reactive constructs.} It is a
synchronous program with 5 exact wait statements.

\hj{ Printer is an example from~\cite{Schneider:1999:CRT:555233}, which
models a printer and a spooler in timed CSP. Its operation can be
described as follows: as soon as the spooler receives a print job it
passes it to the printer through a channel where actual printing process
take place.} Each spooler and printer process is mapped to a separate
CD. Spooler CD sends a job to the Printer CD between 2.7 to 10.6 ms
after receiving it from the environment (e.g. a user). On the other
hand, Printer CD notifies the environment that it starts printing
between 1.2 to 30.3 ms once it receives the job from the Spooler CD.
Actual print job is started between 5.6 to 100.2 ms after the
notification. In this example, bounded wait ensures that both; channel
communication and print job should occur within the specified amount of
time. This example along with HRTCS demonstrates the use of non exact
wait statements.

AECS (Access and Environmental Control System) is an application that
controls an intelligent room environment described in~\cite{aecs_ispa}.
AECS has 2 CDs; CD1 consist of a single wait statement, while CD2 has 2
wait statements. The system is designed to measure how long the entrance
door to the room is being opened or to detect unknown entries (i.e.
intruders). For instance, the system triggers an alarm 10 seconds after
detection of an intruder or generates a beep sound when an entrance door
is being opened for the same amount of time. In the original AECS, the
system needed to interacts with two external timers through input/output
signals in order to wait for a specific amount of time (e.g.
\texttt{TimerTriggered} in Figure~\ref{delaycode:a}). When the timer
expires, it notifies the system through the input signal
\texttt{TimeOut}, which is polled using the \texttt{await} statement.
The program has been modified such that the wait constructs replace
external timers and corresponding interface (I/O) signals, which is
shown in Figure~\ref{delaycode:b}.  With the new wait constructs, these
timers are not necessary and waits can be expressed directly in the
code.

@@

@@

\begin{figure}[h!]
	\centering
\begin{tikzpicture}[scale=0.9]
	\begin{axis}[
			ybar,xtick=data,
			symbolic x
			coords={HRTCS,Printer/CD1,Printer/CD2,AECS/CD2},
			height=5cm,
			width=9.5cm,
			minor y tick num=1,
			yminorgrids=true,
			ymajorgrids=true,
			ytick={0,0.5,...,2},
			enlarge x limits=0.3,
%      xlabel=Benchmark,
			x tick label style={rotate=45,font=\footnotesize},
			ylabel=Difference factor,
		]
			\addplot + [black,fill=white,postaction={pattern=north east lines}] coordinates
			{(HRTCS,1)(Printer/CD1,1)(Printer/CD2,1)(AECS/CD2,1.94)};
			\addplot + [black,fill=white,postaction={pattern=north west
                          lines}] coordinates 
                        {(Printer/CD2, 1)(AECS/CD2, 1.94)};
	\end{axis}
\end{tikzpicture}
\begin{tikzpicture}[scale=0.9]
	\begin{axis}[
			ybar,xtick=data,
			symbolic x coords={Motor},
			ytick={0,0.5,...,5},
			ymin={1.5},
			minor y tick num=1,
			yminorgrids=true,
			ymajorgrids=true,
%      extra y ticks={2.5},
%      extra y tick labels={asdf},
%      extra y tick style={grid=major},
			height=5cm,
			width=9.5cm,
			xlabel=Benchmark,
			xlabel shift={4pt},
			ylabel=Difference factor,
			legend style={
				anchor=north,
				at={(0.45,-0.44)},
				legend columns=-1,
			}
%      nodes near coords
		]
			\addplot + [black,fill=white,postaction={pattern=north east lines}] coordinates
                        {(Motor, 2.60)};
			\addplot + [black,fill=white,postaction={pattern=north west lines}] coordinates
                        {(Motor, 2.63)};
			\addplot + [black,fill=white,postaction={pattern=dots}] coordinates
                        {(Motor, 4.39)};
			\addplot + [black,fill=white,postaction={pattern=horizontal lines}] coordinates
                        {(Motor, 2.92)};
			\addplot + [black,fill=white,postaction={pattern=crosshatch}] coordinates
                        {(Motor, 2.69)};
			\legend{Delay1,Delay2,Delay3,Delay4,Delay5}
	\end{axis}
\end{tikzpicture}
\caption{Accuracy of the results}
\label{fig:graph1}
\end{figure}

@@

\begin{figure}[ht!]
	\centering
%\begin{tikzpicture}[scale=0.9]
%  \begin{axis}[
%      ybar,xtick=data,
%      symbolic x
%      coords={AECS/CD2},
%      height=5cm,
%      width=9.5cm,
%      minor y tick num=1,
%      yminorgrids=true,
%      ymajorgrids=true,
%      xlabel=Benchmark,
%      ylabel=Percentage reduction,
%    ]
%      \addplot coordinates
%      {(AECS/CD2, 11.82)};
%  \end{axis}
%\end{tikzpicture}
\begin{tikzpicture}[scale=0.9]
	\begin{axis}[
			ybar,xtick=data,
			symbolic x coords={Motor,AECS/CD2},
			ytick={0,1,...,12},
			ymin={6},
			minor y tick num=1,
			enlarge x limits=0.5,
			enlarge y limits=0.1,
			yminorgrids=true,
			ymajorgrids=true,
			height=7cm,
			width=9.5cm,
			xlabel=Benchmark,
			xlabel shift={4pt},
			ylabel=Percentage reduction (\%),
			legend style={
				anchor=north,
				at={(0.45,-0.29)},
				legend columns=-1,
			}
		]
			\addplot + [black,fill=white,postaction={pattern=north east lines}] coordinates
                        {(Motor, 8.05) (AECS/CD2, 11.82)};
			\addplot + [black,fill=white,postaction={pattern=north west lines}] coordinates
                        {(Motor, 8.00) (AECS/CD2, 11.82)};
			\addplot + [black,fill=white,postaction={pattern=dots}] coordinates
                        {(Motor, 6.42)};
			\addplot + [black,fill=white,postaction={pattern=horizontal lines}] coordinates
                        {(Motor, 7.53)};
			\addplot + [black,fill=white,postaction={pattern=crosshatch}] coordinates
                        {(Motor, 7.89)};
			\legend{Delay1,Delay2,Delay3,Delay4,Delay5}
	\end{axis}
\end{tikzpicture}
\caption{Reduction in upper bound relaxation with improved WCRT}
\label{fig:graph2}
\end{figure}
